Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-10 paper.tex
Updated the template to Frontiers model

\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
\usepackage{times} % Required package for HRI journal format

% UTF8 support
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx}
\graphicspath{{figs/}}
\usepackage{tikz}
\usetikzlibrary{shapes}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage[numbers, square, comma, sort&compress]{natbib}
\usepackage{multirow}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{textcomp}

@@

\rightheader{Journal of Human-Robot Interaction}
\leftheader{Fink et al.}

@@

\title{On the Dynamics of Anthropomorphism in Robotics
}

\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
              CH-1015 Lausanne, Switzerland
}

@@

\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}

\begin{document}
\maketitle

@@

\paragraph{Anthropomorphism in robotics \hl{[I think this first paragraph should go somewhere else, later probably]}}

@@

\begin{description}
    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}

\end{description}

@@

\begin{description}
	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{description}

@@

\section{Bibliography}
\bibliography{dynamics-anthropomorphism}   % name your BibTeX data base

\hrule

\vspace*{.1in}
Authors' names and contact information: Julia Fink {\tt julia.fink@epfl.ch}, Séverin Lemaignan {\tt severin.lemaignan@epfl.ch}, Pierre Dillenbourg {\tt pierre.dillenbourg@epfl.ch}, CHILI Lab, EPFL, Lausanne, Switzerland.
\end{document}

>>>>

\documentclass{frontiersSCNS} % for Science articles

%\usepackage[utf8x]{inputenc}
%\usepackage[T1]{fontenc}

%\usepackage[english]{babel}

\usepackage{graphicx}
\graphicspath{{figs/}}
\usepackage{tikz}
\usetikzlibrary{shapes}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage{multirow}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{textcomp}

@@

@@

% Leave a blank line between paragraphs in stead of using \\

\copyrightyear{}
\pubyear{}

\def\journal{Cognitive Science}%%% write here for which journal %%%
\def\DOI{}
\def\articleType{Research Article}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Fink {et~al.}} %use et al only if is more than 1 author
\def\Authors{Julia Fink\,$^{*}$, S\'{e}verin Lemaignan\, Claire Braboszcz and Pierre Dillenbourg}
\def\Address{Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland}
\def\corrAuthor{Julia Fink \vspace{1mm}}
\def\corrAddress{EPFL - CHILI, RLC D1 740, Station 20, CH-1015 Lausanne, Switzerland}
\def\corrEmail{julia.fink@epfl.ch}

\begin{document}
\onecolumn
\firstpage{1}

\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.

\maketitle

@@

%\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}

@@

\paragraph{Anthropomorphism in robotics}
\hl{[I think this first paragraph should go somewhere else, later probably]}

@@

\begin{itemize}
    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}

\end{itemize}

@@

\begin{itemize}
	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}

@@

\section{Bibliography}

\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
\bibliography{dynamics-anthropomorphism}   % name your BibTeX data base

\end{document}
